Select-based random access to variable-byte encodings

### 2020-02-28 gradu/msc_english_contents.tex
Fixes

An alternative solution with $select$ data structure is explained in detail and compared to $rank$ by Brisaboa et al. This method does not use data 
reorganizing, but rather capitalizes on the assumption that data is encoded the same way it's in the source. Because variable-byte encoding does not assign 
new codewords to data when encoding, reading the data straight from the memory is much faster than reassembling the word from blocks.

@@

Select data structure works similarly to rank. Index location of every 4096th set bit is stored in the superblock and location of every 64th set bit is stored 
relative to the superblock.

>>>>

An alternative solution with $select$ data structure is proposed and explained in detail later. Comparison to $rank$ by Brisaboa et al is shown with different
implementations of $rank$ and $select$ and several different data sets are used. Proposed method does not use data 
reorganizing, but rather capitalizes on the assumption that data is encoded the same way it is in the source. Because variable-byte encoding does not assign 
new codewords to data when encoding, reading the data straight from the memory is much faster than reassembling the word from blocks.

@@

$Select$ data structure works similarly to rank. Index location of every 4096th set bit is stored in the superblock and location of every 64th set bit is stored 
relative to the superblock. $Select$
